%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
%
%
% Authors:
% Fatih Demirel
%
% License:
% The MIT License
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Fatih Demirel}}}} % First name
	
	\vspace{6pt}
	
	{\Large Computer Engineer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	%\icon{Globe}{11}{\href{http://www.google.com}{portafolio.com}}\\ 
    \icon{Phone}{11}{+90 553 331 83 49}\\
    \icon{MapMarker}{11}{Sivas, Turkey}\\
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\icon{Envelope}{11}{\href{mailto:demirel-fth-93@outlook.com}{demirel-fth-93@outlook.com}}\\	
    \icon{Github}{11}{\href{https://github.com/demirelfth}{github.com/demirelfth}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/fatih-demirel-ab8429111/}{/in/fatih-demirel-ab8429111/}}\\    
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}
 
    %Dummy text
	%\lipsum[1][1-5] \\
        \begin{minipage}[t]{0.83\textwidth}
          I am a software developer with a bachelor's degree in Computer Engineering. I have experience in various programming languages, including JavaScript, Typescript, Java, Python, C++, and PHP. I've worked on software development projects for different companies.
        \end{minipage}
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      JavaScript, Typescript, Java, Python, C, C++, PHP.
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      Matlab, SAS Products, LOGO, Node.js, AWS
    \end{minipage}
    
\end{minipage}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
		{Typescript}
		{Trip Planner}
		{https://github.com/demirelfth/TripPlanner}
		{ A trip planner implemented with using Deutsche Bahn's open API. }
    \entry
		{Typescript, Java}
		{Employee Management System}
		{https://github.com/demirelfth/employee-management-system}
		{ This project developed backend-side with Spring Boot, frontend-side with Angular. }
	\entry
		{Java, Thymeleaf}
		{Student Management System}
		{https://github.com/demirelfth/student-management-system}
		{ Student Management System with Spring Boot and Thymeleaf. }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{09/2013 - 09/2023}
		{ Computer Engineering }
		{Istanbul Technical University}
		{Bachelor's Degree in Computer Engineering}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
        {02/2023 -- Present}
		{Backend Developer}
		{Nişancı Software}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item { Project of Nişancı Sotware is YEBEA and it is about meal delivery service like "Yemek Sepeti". I am working as backend developer at Nişancı Software. }
            \item { Implemented YEBEA's backend with javascript and Node.js.}
        \end{itemize} 
        \texttt{Node.js} \slashsep \texttt{Javascript} \slashsep \texttt{PostgreSQL}}
        \entry
        {03/2023 -- Present}
		{IT Specialist}
		{Metfamer AŞ}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item { Worked on LOGO product tables and background information. }
            \item { Windows Server System with access point, firewall, storage, NAS, VMware researched and learned. }
            \item { Worked as designer with Adobe Illustrator, Adobe Photoshop, CapCut. }
        \end{itemize} 
        \texttt{LOGO} \slashsep \texttt{Windows Server 2022} \slashsep \texttt{T-SQL} \slashsep \texttt{.Net}}
	\entry
		{07/2019 -- 10/2021}
		{Software Engineer}
		{Sade Yazılım ve Danışmanlık}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item { Implemented interface-FWI (Federation Server Web Interface)- with idea of AWI. However, they have different architectures. }
            \item { Implemented interface-AWI (Angular Web Interface)- for clients to use SAS Products' abilities without develop any SAS Code. Angular and Bootstrap used for frontend, Nodejs used for interlayer and PostgreSQL used as database. }
            \item { Worked as Data Management Specialist,therefore researched and learned SAS Code and also SAS products like Dataflux Data Management Server, SAS Federation Server. }
        \end{itemize} 
        \texttt{Angular}\slashsep \texttt{Typescript} \slashsep \texttt{Javascript} \slashsep \texttt{Node.js} \slashsep \texttt{SAS Products} \slashsep \texttt{PostgreSQL} \slashsep \texttt{Bootstrap} }
	\entry
		{02/2018 -- 11/2018 }
		{Full-Stack Developer}
		{Hyplit}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item { Project of Hyplit was about social network like "Wattpad". I worked as full stack developer at Hyplit. }
            \item { Developed this project with HTML, CSS, Bootstrap, Javascript for frontend and PHP  for backend and MySql as database. }
        \end{itemize} 
        \texttt{PHP} \slashsep \texttt{Bootstrap} \slashsep \texttt{MySql}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
	\cvsect{Languages}
    \vspace{-6pt}
    
    \hspace{26mm} \textbf{English} - B2, \textbf{ Turkish} - native

%----------------------------------------------------------------------------------------

\end{document}
